Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2023-01-10 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Co-authored-by: Juan Julián Merelo Guervós <jjmerelo@gmail.com>

As mentioned, the graphs on the left-hand side represent the Pearson's
residuals, showing the difference between the observed and the expected values
for each cell. Thus, large residuals indicate that variables are not truly
independent. In our case, blue shows positive contributions and red negative
contributions to the test. Additionally, the saturation shows how large the
contribution is in contrast to the expected value by chance. 
Tables on the right side show adjusted standardized residuals that according to
\cite{agresti2013categorical}, if greater than +/-2 for cases with few cells,
indicates lack of fit of $H_0$ (in boldface in our table). Complementarily, the
table also shows the percentage of contribution to the test of each cell
(the highest percentage per column also in boldface).

>>>>

As mentioned, the graphs on the left-hand side represent the Pearson's
residuals, showing the difference between the observed and the expected values
for each cell. Thus, large residuals indicate that variables are not truly
independent. In our case, blue shows positive contributions and red negative
contributions to the test. Additionally, the saturation shows how large the
contribution is in contrast to the expected value by chance. 
Tables show on the right hand side adjusted standardized residuals that according to
\cite{agresti2013categorical}, if greater than +/-2 for cases with few cells,
indicate lack of fit of $H_0$ (in boldface in our table). Complementarily, the
table also shows the percentage of contribution to the test of each cell
(the highest percentage per column also in boldface).
